Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-02 paper/paper.tex
update affiliation 1

\address[id=aff1]{%                           % unique id
  \orgname{Department of Zoology, Cambridge}, % university, etc
  \street{Waterloo Road},                     %
  %\postcode{}                                % post or zip code
  \city{London},                              % city
  \cny{UK}                                    % country
}
\address[id=aff2]{%
  \orgname{Marine Ecology Department, Institute of Marine Sciences Kiel},
  \street{D\"{u}sternbrooker Weg 20},
  \postcode{24105}
  \city{Kiel},
  \cny{Germany}
}
\address[id=ccm]{%
  \orgname{Center for Computational Mathematics, Flatiron Institute},
  \street{162 5th Avenue},
  \city{New York, NY 10010},
  \cny{USA}
}

@@

\begin{abstract}

The notion of musical timbre have been extensively considered through the lens of the classic instrumentarium. For such a purpose, datasets of instruments played \textit{ordinario} are considered. On thoses datasets, computational model of timbre considering static spectral features such as Mel Frequency Cepstral coefficents displayed excellent performance.

The availability of richer musical datasets with many playing techniques, allows us to consider computational modeling of musical timbre with the outcomes of recent study  that stresses the importance of long term modulations in auditory perception.

We propose a timbre model that is based on a parametrized...

This model is evaluated in a retrieval task using a perceptually defined retrieval objective. Computational experiments demonstrates 1) the importance of handling long term modulations both in time and frequency, with a gain of $14\%$ in precision compared to Mfccs  2) the relevance of a learned layer that is able provide an average gain of $3\%$ in precision with a reduction of the variance of the prediction error of a factor of 2.

\end{abstract}

>>>>

\address[id=aff1]{%                           % unique id
  \orgname{Music and Audio Research Lab, New York University}, % university, etc
  \street{370 Jay Street},                     %
  %\postcode{}                                % post or zip code
  \city{New York, NY},                              % city
  \cny{USA}                                    % country
}
\address[id=aff2]{%
  \orgname{Marine Ecology Department, Institute of Marine Sciences Kiel},
  \street{D\"{u}sternbrooker Weg 20},
  \postcode{24105}
  \city{Kiel},
  \cny{Germany}
}
\address[id=ccm]{%
  \orgname{Center for Computational Mathematics, Flatiron Institute},
  \street{162 5th Avenue},
  \city{New York, NY 10010},
  \cny{USA}
}

@@

\begin{abstract}
Abstract here.
\end{abstract}
